
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r Load Packages, include=FALSE}
library(ggplot2)
library(knitr)
library(readxl)
library(dplyr)
library(magrittr)
library(latexpdf)
library(pandocfilters)
```
```{r Load File, include=FALSE}
load(file = 'C:/Users/sbadhani/Desktop/R Studio Assigments/Basetable_Gambling.Rdata')
```

```{r Read File, include=FALSE}
DataMart_Description<-read_excel("C:/Users/sbadhani/Desktop/R Studio Assigments/DataMart_Description.xlsx")
```


### This is R Markdown marketing Analysis report. It's an automatic report that will change every time when the data is updated. 


The report displays some important information and stats about the Gambling data countrywise, Age wise and other factors of the Gamblers. 



The Below Information shows the marketing metrics for the betting company


```{r, echo = FALSE}
Gambling_Stats = Basetable_Gambling %>% 
    dplyr::summarise(
    Max_Gain=round(max(Total_Profit_Gambling,na.rm=TRUE)),
    Max_Bets = round(max(Total_Bets_Gambling,na.rm=TRUE)),
    Max_Stakes = round(max(Total_Stakes,na.rm=TRUE)),
    Max_Winnings = round(max(Total_Winnings,na.rm=TRUE)),
    Min_Gain=round(min(Total_Profit_Gambling,na.rm=TRUE)),
    Min_Bets = round(min(Total_Bets_Gambling,na.rm=TRUE)),
    Min_Stakes = round(min(Total_Stakes,na.rm=TRUE)),
    Min_Winnings = round(min(Total_Winnings,na.rm=TRUE)),
    Mean_Gain=round(mean(Total_Profit_Gambling,na.rm=TRUE)),
    Mean_Bets = round(mean(Total_Bets_Gambling,na.rm=TRUE)),
    Mean_Stakes = round(mean(Total_Stakes,na.rm=TRUE)),
    Mean_Winnings = round(mean(Total_Winnings,na.rm=TRUE)),
    Mean_Gain=round(sd(Total_Profit_Gambling,na.rm=TRUE)),
    Mean_Bets = round(sd(Total_Bets_Gambling,na.rm=TRUE)),
    Mean_Stakes = round(sd(Total_Stakes,na.rm=TRUE)),
    Mean_Winnings = round(sd(Total_Winnings,na.rm=TRUE)),
    Frequency = round(sum(Total_No_Days_Played_Gambling,na.rm=TRUE)),
    Gamblers=length(unique(UserID)))

knitr:: kable(Gambling_Stats)
```



The Below Information shows the TOP 10 Country that has generated high Profit   

```{r, echo = FALSE}

 
 countryRmark = 
 Basetable_Gambling %>% 
 dplyr::group_by (Country_Name)%>% 
 dplyr::summarise(
       Total_Profit=round(sum(!is.na(Total_Profit_Gambling))),
       Profit_margin=sum(Total_Profit_Margin_Pcnt),
       Age = round(mean(AGE,na.rm=TRUE),0),
       TotalBets = round(sum(!is.na(Total_Bets_Gambling))),
       TotalStakes = round(sum(!is.na(Total_Stakes))),
       TotalWinnings = round(sum(!is.na(Total_Winnings))),
       Frequency_Played = round(sum(!is.na(Total_No_Days_Played_Gambling))),
       Gamblers=length(unique(UserID)))

countryRmark = countryRmark[order(-countryRmark$Total_Profit),]

knitr:: kable(countryRmark[1:10,])
```




The Below Information shows the Profit made by each Age group 

```{r, echo = FALSE}
Age_Group<-   Basetable_Gambling %>% 
              dplyr::group_by (Age_Group)%>% 
              dplyr::summarise(
               Total_Profit=round(sum(!is.na(Total_Profit_Gambling))),
               Profit_margin=sum(Total_Profit_Margin_Pcnt),
               Age = round(mean(AGE),0),
               TotalBets = round(sum(!is.na(Total_Bets_Gambling))),
               TotalStakes = round(sum(!is.na(Total_Stakes))),
               TotalWinnings = round(sum(!is.na(Total_Winnings))),
               Frequency_Played = round(sum(!is.na(Total_No_Days_Played_Gambling))),
               Gamblers=length(unique(UserID)))

Age_Group = Age_Group[order(-Age_Group$Total_Profit),]

knitr:: kable(Age_Group[1:5,])
```


### Top 5 Number of Gamblers per Age Group : 

```{r, echo = FALSE}
 Gamblers_perAge = Basetable_Gambling %>% 
                    dplyr::group_by (Age_Group)%>% 
                    dplyr::summarise(
                    Gamblers=length(unique(UserID)))


Gamblers_perAge = Gamblers_perAge[order(Gamblers_perAge$Gamblers),]
Gamblers_perAge = Gamblers_perAge[1:5,]
Gamblers_perAge = Gamblers_perAge[order(Gamblers_perAge$Gamblers),]



ggplot(data = Gamblers_perAge, aes(x=`Age_Group`, y= Gamblers)) + 
  geom_bar(stat = "identity") +
  coord_flip() + labs(title="Number of Gamblers per Age Group", x="Age_Group", y="Number of Gamblers")
```


###The Below Information shows the Top 10 Profit achieved per Language 

```{r, echo = FALSE}
LanguageRMark<-   Basetable_Gambling %>% 
              dplyr::group_by (Language_Description)%>% 
              dplyr::summarise(
               Total_Profit=round(sum(!is.na(Total_Profit_Gambling))),
               Profit_margin=sum(Total_Profit_Margin_Pcnt),
               Age = round(mean(AGE),0),
               TotalBets = round(sum(!is.na(Total_Bets_Gambling))),
               TotalStakes = round(sum(!is.na(Total_Stakes))),
               TotalWinnings = round(sum(!is.na(Total_Winnings))),
               Frequency_Played = round(sum(!is.na(Total_No_Days_Played_Gambling))),
               Gamblers=length(unique(UserID)))

LanguageRMark = LanguageRMark[order(-LanguageRMark$Total_Profit),]

knitr:: kable(LanguageRMark[1:10,])
```



### Number Of Gamblers per Application:

```{r, echo = FALSE}
 ApplicationRmark = Basetable_Gambling %>%
                    dplyr::group_by(Application_Description) %>%
                    dplyr::summarise(
                    Total_Profit=round(sum(!is.na(Total_Profit_Gambling))),
                    Gamblers=length(unique(UserID)))


ApplicationRmark = ApplicationRmark[order(-ApplicationRmark$Gamblers),]
ApplicationRmark = ApplicationRmark[1:5,]
ApplicationRmark = ApplicationRmark[order(-ApplicationRmark$Gamblers),]



ggplot(data = ApplicationRmark, aes(x=`Application_Description`, y= Gamblers)) + 
  geom_bar(stat = "identity") +
  coord_flip() + labs(title="Number of users per Application", x="Application", y="Number of Gamblers")
```


### Number Of Loyal Gamblers and their status:


```{r, echo = FALSE}
 LoyaltyRmark = Basetable_Gambling %>% 
                    dplyr::group_by (Loyalty_Status)%>% 
                    dplyr::summarise(
                    Gamblers=length(unique(UserID)))


LoyaltyRmark = LoyaltyRmark[order(-LoyaltyRmark$Gamblers),]
LoyaltyRmark = LoyaltyRmark[1:3,]
LoyaltyRmark = LoyaltyRmark[order(-LoyaltyRmark$Gamblers),]



ggplot(data = LoyaltyRmark, aes(x=`Loyalty_Status`, y= Gamblers)) + 
  geom_bar(stat = "identity") +
  coord_flip() + labs(title="Number of Gamblers per Loyalty", x="Loyalty_Status", y="Number of Gamblers")
```


### Most Played day of the Sports Gambling:


```{r, echo = FALSE}
 SportsRmark = Basetable_Gambling %>% 
                    dplyr::group_by (MostPlayed_Day_Sp)%>% 
                    dplyr::summarise(
                    Gamblers=length(unique(UserID)))


SportsRmark = SportsRmark[order(-SportsRmark$Gamblers),]
SportsRmark = SportsRmark[1:7,]
SportsRmark = SportsRmark[order(-SportsRmark$Gamblers),]



ggplot(data = SportsRmark, aes(x=`MostPlayed_Day_Sp`, y= Gamblers)) + 
  geom_bar(stat = "identity") +
  coord_flip() + labs(title="Number of Gamblers per Day", x="Days_Played", y="Number of Gamblers")
```

### Most Played Month of the Sports Gambling:


```{r, echo = FALSE}
 Sports_Month = Basetable_Gambling %>% 
                    dplyr::group_by (Most_Played_Month_Sp)%>% 
                    dplyr::summarise(
                    Gamblers=length(unique(UserID)))

Sports_Month = Sports_Month[1:8,]

ggplot(data = Sports_Month, aes(x=`Most_Played_Month_Sp`, y= Gamblers)) + 
  geom_bar(stat = "identity") +
  coord_flip() + labs(title="Number of Gamblers per Month", x="Month", y="Number of Gamblers")
```


### Most Played day of the Casino:


```{r, echo = FALSE}
Casino = Basetable_Gambling %>% 
                    dplyr::group_by (MostPlayed_Day_Ca)%>% 
                    dplyr::summarise(
                    Gamblers=length(unique(UserID)))

Casino = Casino[1:7,]


ggplot(data = Casino, aes(x=`MostPlayed_Day_Ca`, y= Gamblers)) + 
  geom_bar(stat = "identity") +
  coord_flip() + labs(title="Number of Gamblers per Day", x="Days_Played", y="Number of Gamblers")
```

### Most Played day of the Games:


```{r, echo = FALSE}
Games = Basetable_Gambling %>% 
                    dplyr::group_by (MostPlayed_Day_Ga)%>% 
                    dplyr::summarise(
                    Gamblers=length(unique(UserID)))

Games = Games[1:7,]


ggplot(data = Games, aes(x=`MostPlayed_Day_Ga`, y= Gamblers)) + 
  geom_bar(stat = "identity") +
  coord_flip() + labs(title="Number of Gamblers per Day", x="Days_Played", y="Number of Gamblers")
```


### Most Played day of the Poker:


```{r, echo = FALSE}
Poker = Basetable_Gambling %>% 
                    dplyr::group_by (Most_Played_Day_Po)%>% 
                    dplyr::summarise(
                    Gamblers=length(unique(UserID)))

Poker = Poker[1:7,]


ggplot(data = Poker, aes(x=`Most_Played_Day_Po`, y= Gamblers)) + 
  geom_bar(stat = "identity") +
  coord_flip() + labs(title="Number of Gamblers per Day", x="Days_Played", y="Number of Gamblers")
```




### Datamart & variables description:

The datamart(basetable) was created by merging four differents files: Demographics, UserDailyAggregation,PokerChipConversions and ActualSportsGambling. 

The Datamart consist of the important marketing metrics for the betting company and the behaviour of each unique user.

The below information is the description of each variable in the datamart which has been used in visualization and can help in making marketing strategy.


```{r,  echo = FALSE}
kable(DataMart_Description)
```


